---
title: "Differences in Differences"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{did}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic Example Code

\code{QEDinfR} provides functions which make basic Difference in Differences designs easy and quick. After specifying your model, the plot method for \code{qed_did} objects quickly creates trend lines, allowing you to visualise the results.  

```{r setup}
library(QEDinfR)
data(banks)
```

First we run the example code model.

```{r}
fit <- qed_did("num_banks_in_business", "year", 1930,  "bank_district", "6th district", df = banks)
summary(fit)
```

Next, we plot the trend lines for the treatment and control group from pre-treatment to post-treatment. 
```{r}
plot(fit)
```
The above graph allows us to visualise the disparity in differences between the treatment group and control group from one time period (i.e. pre-treatment) to the next time period (i.e. post treatment). 
