---
title: "Greedy Matching Methods"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Greedy Matching Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic Example Code

\code{QEDinfR} provides functions which make basic Greedy Matching methods and eventual Outcome analysis easy and quick. Using the \code{qed_match}, we first perform Greedy matching (with or without a specified caliper and with or without replacement while matching) using either Propensity Scores (calculated through a fitted logistic regression) or Mahalanobis Distances (the square root of the sum of the squared distances of each covariate scaled by the covariance matrix). 

```{r setup}
library(QEDinfR)
data(lalonde)
```

## Propensity Score Matching (categorical outcome)

First, we demonstrate how to perform Greedy Matching using Propensity Scores with a categorical outcome of interest.

```{r}
lalonde$nodegr <- factor(lalonde$nodegr)
ps_match <- qed_match(treat ~ age + educ + black, "nodegr", lalonde, "propensityscore", caliper = NULL, replace = FALSE)
summary(ps_match)
```

From the above summary statistics, we see that Greedy Matching using Propensity Scores has reduced the Standardized Mean Differences (SMD) between the control group and treatment group on all included covariates. Following the general rule of thumb that SMD values < 0.1 are desirable, this data is now ready to perform outcome analysis on. 

```{r}
test.qed_match(ps_match)
```

Given that the variable of interest was categorical (whether or not a person had attained a highschool diploma), we perform a Mcnemar test to check for odds ratios between the control group and treatment group with respect to the outcome variable, 'nodegr'.

From the results, we see that the association is significant at the 0.05 level, and people in the treated group are 0.4167 times as likely to not obtain a highscool degree. 

## Mahalanobis Distance Matching (numeric outcome)

Next, we demonstrate how to perform Greedy Matching, using a caliper and without replacement, with a numeric outcome of interest. 
```{r}
md_match <- qed_match(treat ~ age + educ + black, "re78", lalonde, "mahalanobis", caliper = NULL, replace = FALSE)
summary(md_match)
```

From the above summary statistics, we see that Greedy Matching using Propensity Scores has reduced the Standardized Mean Differences (SMD) between the control group and treatment group on all included covariates. Following the general rule of thumb that SMD values < 0.1 are desirable, this data is now ready to perform outcome analysis on. 

```{r}
test.qed_match(md_match)
```

We use a paired t-test to test for a significant association between real earnings in 1978, 're78', and whether the person belonged to the treatment group or control group. From the results above, we see that the association was significant at the 0.05 level (in fact, p < 0.01). A person that received treatment, on average, made $2053.79 lesser in real earnings than a person that hadn't in the year 1978. 
